---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# s7bugreport

The goal of this repository is to demonstrate a potential bug found in S7.

The bug occurs when you have an S7 class (foo) and S3 class (bar) coexisting in a package, and both classes have `$`-extraction methods.

```{r}
library(S7)
foo <- new_class("foo", properties = list(x = new_property(class_integer, default = 10L)))

bar <- function() {
  structure(list(x = 10L), class = "bar")
}

method(`$`, foo) <- function(x, ...) {
  cat("foo $-extraction\n")
  prop(x, ...)
}

`$.bar` <- function(x, ...) {
  cat("bar $-extraction\n")
  .subset2(x, ...)
}
```

Both of these `$`-extraction methods work fine.

```{r}
foo()$x
bar()$x
```

However, when declaring the same classes and methods from a package, the `$.bar` method seems to get discarded.
To ensure that this is run in a clean session, I'll use {reprex} to demonstrate.
Please note in the final chunk that the `"bar $-extraction"` string is missing.

```{r, results='asis'}
rpx <- reprex::reprex({
  library(s7bugreport)
  foo()$x
  bar()$x
})
cat(rpx, sep = "\n")
```

